Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-30 paper/reply.tex
added [Novelty, #1/#2/#3]

\noindent  As far as we know, the present synthesis approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.
This work is the first to address FWL uncertainties based on CEGIS in the digital controller synthesis phase.

@@

\noindent We have evaluated our approach using standard benchmarks taken mostly from the classical control literature [3,15,21,22,35]. Note that the used benchmarks are typically from existing work on control system verification. Larger benchmarks would strengthen our claims; however, related work on controller verification typically considers even smaller benchmarks (cf. 3.5 and 4.1).  Additionally, we only state the winning back-end in the results table, annotating where the one-stage engine was faster. The two order of magnitudes were measured empirically, since the one-stage engine times out on the majority of benchmarks.

>>>>

\noindent  As far as we know, the present synthesis approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.
This work is the first one to address FWL uncertainties based on CEGIS for synthesizing correct-by-design linear stabilizing digital controllers with fixed-point arithmetic for linear
continuous-time plants.

@@

\noindent We have evaluated our approach using standard benchmarks taken mostly from the classical control literature [3,15,21,22,35]. Note that the used benchmarks are typically from existing work on control system verification. Larger benchmarks would strengthen our claims; however, related work on controller verification typically considers even smaller benchmarks (cf. 3.5 and 4.1). We only state the winning back-end in the results table, annotating where the one-stage engine was faster. The two order of magnitudes were measured empirically, since the one-stage engine times out on the majority of benchmarks. Additionally, we did include an upper bound for both the bit width and execution time. Given an arbitrarily high precision and given unlimited execution time, the engine will always succeed.
